---
title: "HW6"
output: github_document
---

This is my response to HW 6:

```{r setup, include=FALSE}
library(tidyverse)
library (patchwork)
library(readr)
library(broom)
library(viridis)
library(dbplyr)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```
We start off by downloading the data from The Washing Post, on on homicides in 50 large U.S. cities via Github. After taking a look at the dataset, we also created city_state variable and a binary variable indicating whether the homicide is solved.
```{r}
homicide_df =
  read.csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")) %>%
  janitor::clean_names() 

skimr::skim(homicide_df)
  
homicide_df$city_state= 
  paste(homicide_df$city,",", homicide_df$state)


homicide_df = 
  homicide_df %>%
  filter(city_state != "Dallas , TX" | #drop certain cities
        city_state != "Phoenix , AZ" |
        city_state != "Kansas City , MO" |
        city_state != "Tulsa , AL") %>% 
  filter(victim_race == "White" | #drop rows not containing white or black in victim_race
           victim_race == "Black") %>%
  mutate(resolved = as.numeric(disposition == 'Closed by arrest'), #create a binary resolved variable
         victim_age=as.numeric(victim_age)) #change victim age as numeric
```
For the city of Baltimore, MD...  
``` {r baltimore}
baltimore_df = 
  homicide_df %>%
  filter(city == "Baltimore") %>%
  mutate(
    victim_race=fct_relevel(victim_race, "White")) %>%
  select(resolved, victim_age, victim_sex, victim_race)
```
using glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. 
``` {r create a logistic regression with glm function}
fit_logistic = 
  baltimore_df %>%
  glm(resolved ~victim_age + victim_race + victim_sex, data =.,
      family = binomial)
conf = confint(fit_logistic)

```
Obtaining the estimate, CI, OR for solving homicides comparing non-white victims to white victims keeping all other variables fixed:
```{r table}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  select(term, log_OR = estimate, OR, p.value) %>% 
  knitr::kable(digits = 3)
```
Homicides in which the victim is black are substantially less likely to be resolved that those in which the victim is white

Using the prop.test on Baltimore, MA
``` {r baltimore data, error = TRUE}
prop.test(
  homicide_status_df %>% filter(city_state == "Baltimore , MD") %>% pull(unsolved_hom), 
  homicide_status_df %>% filter(city_state == "Baltimore , MD") %>% pull(total_hom)) %>% 
  broom::tidy()
```
Applying prop.test on all the cities
