---
title: "HW6"
output: github_document
---

This is my response to HW 6:

```{r setup, include=FALSE}
library(tidyverse)
library (patchwork)
library(readr)
library(broom)
library(viridis)
library(dbplyr)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```
We start off by downloading the data from The Washing Post, on on homicides in 50 large U.S. cities via Github. After taking a look at the dataset, we also created city_state variable and a binary variable indicating whether the homicide is solved.
```{r}
homicide_df =
  read.csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")) %>%
  janitor::clean_names() 

skimr::skim(homicide_df)
  
homicide_df$city_state= 
  paste(homicide_df$city,",", homicide_df$state)


homicide_df = 
  homicide_df %>%
  filter(city_state != "Dallas , TX" | #drop certain cities
        city_state != "Phoenix , AZ" |
        city_state != "Kansas City , MO" |
        city_state != "Tulsa , AL") %>% 
  filter(victim_race == "White" | #drop rows not containing white or black in victim_race
           victim_race == "Black") %>%
  mutate(resolved = as.numeric(disposition == 'Closed by arrest'), #create a binary resolved variable
         victim_age=as.numeric(victim_age)) #change victim age as numeric
```
For the city of Baltimore, MD...  
``` {r baltimore}
baltimore_df = 
  homicide_df %>%
  filter(city == "Baltimore") %>%
  mutate(
    victim_race=fct_relevel(victim_race, "White")) %>%
  select(resolved, victim_age, victim_sex, victim_race)
```
using glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. 
``` {r create a logistic regression with glm function}
fit_logistic = 
  baltimore_df %>%
  glm(resolved ~victim_age + victim_race + victim_sex, data =.,
      family = binomial) %>%
  broom::tidy()
```
Obtaining the estimate, CI, OR for solving homicides comparing non-white victims to white victims keeping all other variables fixed:
```{r table}
fit_logistic %>% 
    group_by(term) %>% 
    summarize(
    ci_lower = quantile(estimate, 0.025), 
    ci_upper = quantile(estimate, 0.975))
  
  select(term, log_OR = estimate, OR, p.value) %>% 
  knitr::kable(digits = 3)
```
Interpretation:
Homicides in which the victim is black are substantially less likely to be resolved that those in which the victim is white. Homicides in which the victim is male are significantly less like to be resolved than those in which the victim is female.The effect of age is statistically significant, and should be studied further.

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing Black victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

``` {r}
results_df = 
  homicide_status_df %>% 
  mutate(glm_tests = map2(.x=)
  glm(resolved ~victim_age + victim_race + victim_sex, data =.,
      family = binomial)
    prop_tests = map2(.x = unsolved_hom, .y = total_hom, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low,conf.high)
```
Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
``` {r plot for results_df}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```
